The ChEMBL database as Linked Open Data

### 2012-08-14 article.tex
Removed the bit about providing full detail, because that actually depends on how the URI is resolved. It may also redirect to a publisher's web page for that article.

The literature from which all this data was extracted, is replicated from the database,
but only a subset of the possible information about that literature is provided. In all cases 
the PubMed Identifiers (PMIDs) and Digital Object Identifiers (DOIs) are used to link
to authoritative databases that provide full detail about the references, as outlined later in this paper.
The properties are provided using the BIBO ontology:

>>>>

The literature from which all this data was extracted, is replicated from the database,
but only a subset of the possible information about that literature is provided. In all cases 
the PubMed Identifiers (PMIDs) and Digital Object Identifiers (DOIs) are used to link
to authoritative database, as outlined later in this paper.
The properties are provided using the BIBO ontology:
